Shades of Green

### 2023-09-25 docs/presentations/20230928-sehm_presentation.qmd
update bioeconomy stats to dynamic in sehm_pres

## 817 Innovations in Forest Bioeconomy (Uncleaned)

@@

| @vivien2019HijackingBioeconomy | Type II | Type III | Type I |
|---|---|---|---|
|  | A science-based economy driven   by industrial biotechnology<br>     <br>     The cell is a factory | Biomass replaces fossil fuels   and mining to produce energy and materials<br>     <br>     Biorefining at the heart of ecological transition (multilevel perspective). | An ecological economy, that is   compatible with the biosphere <br>     <br>     Counter-expertise rather than concrete technical solutions Criticism from   social groups who remain at the margins of decisionmaking centers |
| Codes | 1 | 2 | 3 |

>>>>

```{python}
# | label: Sum bioeconomy visions
# | output: asis

sum_bioeconomy_innovations = swinno["bioeconomy"].sum()

display(
    Markdown(
        f"# {sum_bioeconomy_innovations} Innovations in Forest Bioeconomy (Uncleaned){{.inverted}}"
    )
)

@@

| @vivien2019HijackingBioeconomy | Type II | Type III | Type I |
|---|---|---|---|
|  | A science-based economy driven   by industrial biotechnology<br>     <br>     The cell is a factory | Biomass replaces fossil fuels   and mining to produce energy and materials<br>     <br>     Biorefining at the heart of ecological transition (multilevel perspective). | An ecological economy, that is   compatible with the biosphere <br>     <br>     Counter-expertise rather than concrete technical solutions Criticism from   social groups who remain at the margins of decisionmaking centers |
